Results

### 2021-08-18 Analysis/03_Summarise_results.Rmd
Updated results figure and table

```{r, echo = FALSE}
## Creating the list of results
all_results <- list(equalizing   = equalizing,
                    facilitation = facilitation,
                    filtering    = filtering,
                    competition  = competition)
## The different removal level names
removals <- c("20%", "40%", "60%", "80%")
## The colours
cols <- c("blue", "orange", "red", "green")
```

@@

```{r, echo = FALSE}
kable(model_table, caption = "Results of the model scaled metric ~ removal level per stressor", align = "c")
```

```{r, echo = FALSE}
## Even fancier column names
colnames(null_table) <- gsub(".d_rm", ".rm", colnames(null_table))
colnames(null_table) <- gsub("equalizing", "equa", colnames(null_table))
colnames(null_table) <- gsub("facilitation", "faci", colnames(null_table))
colnames(null_table) <- gsub("filtering", "filt", colnames(null_table))
colnames(null_table) <- gsub("competition", "comp", colnames(null_table))
kable(null_table, caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor", align = "c")
```

@@

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
fancy.plot(scaled_results, col = c("blue", "orange"))
```

Figure X1: Simulation results: the y axes represent the different metrics tested (sorted by categories). The different columns represent the different stressors. The x-axes represent the metric values centred on the random changes and scaled by the maximum value for each metric between the four stressors. Negative and positive values signify a decrease/increase in the metric score. The dots represent the median metric value, the full line their 50% confidence interval (CI) and the dashed line their 95% CI. The colours are just here to visually separate the metrics rows but the colour gradient within each row corresponds to a removal of respectively 80%, 60%, 40% and 20% of the data (from top to bottom).

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
fancy.plot(scaled_results, col = c("blue", "orange"), lm = model_fits, null = null_differences)
```

Figure X2: See above + Grey lines in the background are a fitted linear model on the scaled metric score function of removal amount and the value displayed is the adjusted R^2 from each of these models. Dashed grey lines represent non-significant models (slope or/and intercept). The grey line plots represent (CI + median) represent distribution of metrics scores not clearly different from the random metric scores (paired t-test p value > 0.05).

> I think that Figure X2 would do a good summary of how the metrics pick up changes. Here's a couple of interpretations of it in the light of my previous work on which metric to choose:
  * Don't use the TPD richness metric, it doesn't do much.
  * On the other hand, hypervolume regularity and richness are two good metrics because they only pick up really specific changes (respectively "equalizing" and "facilitation") and nothing else.

>>>>

```{r, echo = FALSE}
## Creating the list of results
all_results <- list(equalizing   = equalizing,
                    facilitation = facilitation,
                    filtering    = filtering,
                    competition  = competition)

## Sort the results per name
sort.metrics <- function(one_results, order) {

    ## Get the results table
    all_results <- colnames(one_results$results_table)

    ## Extract the metric names
    metrics <- unique(gsub("stressor_", "", gsub("random_", "", gsub("_rm.*", "", all_results))))

    ## Reorder these names
    metrics <- metrics[order]

    ## Get the removal levels
    levels <- unique(gsub(".*_rm", "", all_results))

    ## Sort the metrics_names
    sorted_metrics <- unlist(lapply(as.list(metrics), function(x, levels) paste(x, levels, sep = "_rm"), levels = levels))
    ## Adding the random/stressor bits
    sorted_metrics <- c(apply(cbind(paste0("random_", sorted_metrics), paste0("stressor_", sorted_metrics)), 1, c))

    ## Match the new column order
    one_results$results_table <- one_results$results_table[, match(sorted_metrics, all_results)]

    ## Return the updated results
    return(one_results)
}

## Re-ordering results for fancyness
new_order <- c(14, 12, 3, 6,
               15, 11, 2, 8,
               7, 4, 5, 13,
               10, 9, 1)
all_results <- lapply(all_results, sort.metrics, order = new_order)

## The different removal level names
removals <- c("20%", "40%", "60%", "80%")
## The colours
cols <- c("blue", "orange", "red", "green")

## Fancier names
fancy_names <- c("TPD[TPD]\nregularity",
                 "hypervolume[BAT]\nregularity",
                 "dendrogram[BAT]\nregularity",
                 "dissimilarity[FD]\nregularity",
                 "TPD[TPD]\ndivergence",
                 "hypervolume[BAT]\ndivergence",
                 "dendrogram[BAT]\ndivergence",
                 "dissimilarity[melodicMPD]\ndivergence(MPD)",
                 "dissimilarity[melodicRao]\ndivergence(Rao)",
                 "dissimilarity[FD]\ndivergence(Rao)",
                 "dissimilarity[FD]\ndivergence",
                 "TPD[TPD]\nrichness",
                 "hypervolume[BAT]\nrichness",
                 "convex hull[BAT]\nrichness",
                 "dendrogram[BAT]\nrichness")
```

@@

```{r, echo = FALSE}
rownames(model_table) <- gsub("\n", "_", fancy_names)
kable(model_table, caption = "Results of the model scaled metric ~ removal level per stressor", align = "c")
```

```{r, echo = FALSE}
rownames(null_table) <- fancy_names
## Even fancier column names
colnames(null_table) <- gsub(".d_rm", ".rm", colnames(null_table))
colnames(null_table) <- gsub("equalizing", "equa", colnames(null_table))
colnames(null_table) <- gsub("facilitation", "faci", colnames(null_table))
colnames(null_table) <- gsub("filtering", "filt", colnames(null_table))
colnames(null_table) <- gsub("competition", "comp", colnames(null_table))
kable(null_table, caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor", align = "c")
```

@@

```{r, fig.width = 8, fig.height = 10, echo = FALSE}
col_vector <- c(rep("blue", 4), # The richness ones
                rep("orange", 7), # The divergence ones
                rep("darkgreen", 4)) # The regularity ones
## The plot
fancy.plot(scaled_results, col = col_vector, lm = model_fits, null = null_differences, metric.names = fancy_names)
```

Figure 1: Simulation results: the y axes represent the different metrics tested (sorted by categories). The different columns represent the different stressors. The x-axes represent the metric values centred on the random changes and scaled by the maximum value for each metric between the four stressors. Negative and positive values signify a decrease/increase in the metric score. The dots represent the median metric value, the full line their 50% confidence interval (CI) and the dashed line their 95% CI. The colours are just here to visually separate the metrics rows but the colour gradient within each row corresponds to a removal of respectively 80%, 60%, 40% and 20% of the data (from top to bottom). Grey lines in the background are a fitted linear model on the scaled metric score function of removal amount and the value displayed is the adjusted R^2 from each of these models. Dashed grey lines represent non-significant models (slope or/and intercept). The grey line plots represent (CI + median) represent distribution of metrics scores not clearly different from the random metric scores (paired t-test p value > 0.05).
